\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
delete word
fix awkard sentence

%%%%%%%%%%%%%%%%% Volume bounding
If a user is creating and placing multiple daughter volumes within a \emph{mother} volume then it is the user's responsibility to create a solid which fully 
encompasses the daughter volumes. Overlaps between daughter volumes and the mother can be detected to, but it is desirable 
% \colorbox{yellow}{It's not just desirable, it's absolutely necessary isn't it?  And I'm not sure what the word ``efficiently'' means precisely in this context.} 
to have a mother volume shape that efficiently holds its daughters. This is not always the case for example assembly volumes.

>>>>

%%%%%%%%%%%%%%%%% Volume bounding
If a user is creating and placing multiple daughter volumes within a \emph{mother} volume then it is the user's responsibility to create a solid which fully 
encompasses the daughter volumes. Overlaps between daughter volumes and the mother can be detected, but it is desirable 
% \colorbox{yellow}{It's not just desirable, it's absolutely necessary isn't it?  And I'm not sure what the word ``efficiently'' means precisely in this context.} 
to have a mother volume shape that efficiently holds its daughters. However, there are exceptions to this rule in the form of assembly volumes.
